\cleardoublepage

\section*{Acknowledgements}

Finally, it is done. If anyone asks, \textit{`What did you do with your life between the ages of 26 and 30?'} I can show them this thesis. I figure, based on a 40 hour working week with a month holiday each year (which may or may not be an accurate estimate), that this represents about 7,680 hours of work. This is short of the Malcolm Gladwell prescribed 10,000 hours supposedly required for success\footnote{It's okay, I wrote these acknowledgements after the examiners meeting so I know that I got a pass.}, so clearly I had more than a small bit of help in getting to this stage. The following list is probably incomplete so sincere apologies if you are not mentioned, you are also awesome!


Perhaps quite naturally this thesis has evolved into a work of two halves. On one side is Prof. Tony Carrington and the work exploring the pairing mechanism in the recently discovered pnictide materials and on the other side is Prof. Nigel Hussey and the work picking apart the fine detail of the cuprate phase diagram. Both supervisors have been outstanding and I would like to thank them for guiding me through the PhD with a great deal of patience and support and for allowing me to spend time at summer schools in weird parts of Europe.


In the early, more prospective, days of the PhD, the workshop staff --- John Rowden, Adrian Crimp, Tim Newbury and Richard Exley --- helped out enormously by building components for the experiments. Richard Exley especially gave lots of help and advice regarding the first two years spent living aboard Greenwood which was hugely appreciated when rain was rotting our windows and rusting our stove. Thanks fellas!

My peers in the CES group have been a stellar bunch of people. These include Dr. Ali Bangura, Dr. Rosie Cooper, Dr. Benoit Faque, Dr. Matt French, Dr. Isabelle Guillamon, Dr. Neil Headings, Dr. Liam Malone, Iioanna Mouzoupoulou, Carsten Putzke, Dr. Alessandro Serafin, Nick Wakeham and Phil Walmsley. I would like to thank Dr. Jon Fletcher for huge amounts of support early on and for being a pretty sound kind of person and Dr. Patrick Rourke and Dr. Jean-Francois Mercure for similar reasons. Special late night, long weekend and drinking credit goes to Dr. Xiaofeng Xu, Dr. Chris Lester and Dr. Caroline Andrew and I owe thanks to Bob Wiltshire and James Kelly for the craic. Outside the group I would also like to thank members of the nano group, members of the IAC and others for ski trips and other general good times during these four years.

Formally, I would like to thank our collaborators Prof. Shibauchi and his group at Kyoto university who grew the \BaFeAsP{} crystals and Prof. Takeuchi and his group at Sendai University for the \acs{BSCO} samples. The first set of high field data taken at the \ac{LNCMI}, Toulouse was taken with the help of Dr. Baptiste Vignolle, Prof. Cyril Proust and Dr. Patrick Rourke. The second set of high field data was taken by Dr. Baptiste Vignolle, Prof. Cyril Proust, Dr. Patrick Rourke, Prof. Nigel Hussey and Dr. Jean-Francois Mercure. The final set of high field data from \ac{HFML}, Nijmegen was taken by Dr. Patrick Rourke, Dr. Alix McCollam, Ioanna Mouzoupoulou and Dr. Xiaofeng Xu. I would also like to acknowledge Dr. Mairi Haddow for help on the x-ray characterisation.

Finally, and most of all, thanks to my family to whom I owe just about everything else.




